---
title: "Final Project EDA"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(mice)
```

```{r}
member = read_csv('data/member-data-2020-stat149.csv')
head(member)
```

```{r}
dim(member)
```
```{r}
member %>% count(MEMTYPE)
```

```{r}
summary(member)

```
```{r}
member %>% 
  count(AnySection)
```
```{r}
member[duplicated(member[,]),]
```


## Visualization
```{r}
ggplot(member, aes(USA.CAN, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("USA.CAN") 

ggplot(member, aes(JSMtot, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("JSMtot") 

ggplot(member, aes(DontPublish, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("DontPublish") 

ggplot(member, aes(MEMTYPE, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("MEMTYPE") 

ggplot(member, aes(Age, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("Age") 

ggplot(member, aes(AgeJoinedASA, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("AgeJoinedASA") 

ggplot(member, aes(Gender, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("Gender") 

ggplot(member, aes(EmploymentCategory, fill = AnySection)) +     
   scale_x_discrete(guide = guide_axis(n.dodge=3))+
   geom_bar(position = 'dodge')+ggtitle("EmploymentCategory") 

ggplot(member, aes(InChapter, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("InChapter") 


```



## Data processing

### Turn char columns to numeric factor values
These columns do not have missing value. We turn yes/no to 1/0.
```{r}
member$AnySection = as.numeric(as.factor(member$AnySection))-1
member$DontPublish = as.numeric(as.factor(member$DontPublish))-1
member$MEMTYPE = as.numeric(as.factor(member$MEMTYPE))-1
member$InChapter = as.numeric(as.factor(member$InChapter))-1
member$P.SEC.BE = as.numeric(as.factor(member$P.SEC.BE))-1
member$P.SEC.BIOM = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.BIOP = as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.CNSL = as.numeric(as.factor(member$P.SEC.CNSL))-1

member$P.SEC.COMP = as.numeric(as.factor(member$P.SEC.COMP))-1
member$P.SEC.EDUC = as.numeric(as.factor(member$P.SEC.EDUC))-1
member$P.SEC.ENVR = as.numeric(as.factor(member$P.SEC.ENVR))-1
member$P.SEC.EPI = as.numeric(as.factor(member$P.SEC.EPI))-1
member$P.SEC.GOVT = as.numeric(as.factor(member$P.SEC.GOVT))-1
member$P.SEC.GRPH = as.numeric(as.factor(member$P.SEC.GRPH))-1

member$P.SEC.HPSS = as.numeric(as.factor(member$P.SEC.HPSS))-1
member$P.SEC.MDD = as.numeric(as.factor(member$P.SEC.MDD))-1
member$P.SEC.MHS = as.numeric(as.factor(member$P.SEC.MHS))-1
member$P.SEC.MKTG = as.numeric(as.factor(member$P.SEC.MKTG))-1
member$P.SEC.NPAR = as.numeric(as.factor(member$P.SEC.NPAR))-1
member$P.SEC.QP = as.numeric(as.factor(member$P.SEC.QP))-1

member$P.SEC.SBSS = as.numeric(as.factor(member$P.SEC.SBSS))-1
member$P.SEC.SDNS= as.numeric(as.factor(member$P.SEC.SDNS))-1
member$P.SEC.SGG = as.numeric(as.factor(member$P.SEC.SGG))-1
member$P.SEC.SI = as.numeric(as.factor(member$P.SEC.SI))-1
member$P.SEC.SIS = as.numeric(as.factor(member$P.SEC.SIS))-1
member$P.SEC.SLDM = as.numeric(as.factor(member$P.SEC.SLDM))-1

member$P.SEC.SOC = as.numeric(as.factor(member$P.SEC.SOC))-1
member$P.SEC.SPES= as.numeric(as.factor(member$P.SEC.SPES))-1
member$P.SEC.SRMS = as.numeric(as.factor(member$P.SEC.SRMS))-1
member$P.SEC.SSPA = as.numeric(as.factor(member$P.SEC.SSPA))-1
member$P.SEC.TSHS = as.numeric(as.factor(member$P.SEC.TSHS))-1

```

### Missing value
USA.CAN column has 12 missing values, which are less than 1% of the total data. We will impute the missing value with the mean of this column.
```{r}
sum(is.na(member$USA.CAN)) 
member$USA.CAN[is.na(member$USA.CAN)] = 'Yes'
# any better way to convert yes/no to 1/0 ??
member$USA.CAN = as.numeric(as.factor(member$USA.CAN))-1
member %>% 
  count(USA.CAN)
```

Gender column has 2834 missing values.
EmploymentCategory column has 4216 missing values.
```{r}
sum(is.na(member$Gender)) 
sum(is.na(member$EmploymentCategory))
```

Impute the missing value of Age and AgeJoinedASA using MICE method. From the pattern matrix, we could see that the missing values in these two columns are systematic.
```{r}
md.pattern(member[,6:7])
```
```{r}
imp <- mice(member, method = "pmm", m = 5, maxit = 50, printFlag = FALSE)
member.imp <- complete(imp)
summary(member.imp)
```

#### Description of member.imp
So far member.imp has JSMtot imputed by mean imputation, Age and AgeJoinedASA imputed by MICE method. Gender and  EmploymentCategory  still have missing values. From the pattern matrix, we see an large overlap of missing values in the two columns.

```{r}
md.pattern(member[,8:9])
```

## Correlation Matrix
```{r}
library("Hmisc")
library(corrplot)

```

```{r}
sub.member.imp =cbind(member.imp[,0:7],member.imp[,10:37])
cor <- cor(as.matrix(sub.member.imp))
corrplot(cor, type = "upper", 
         tl.col = "black", tl.srt = 45)

```
```{r}
# ++++++++++++++++++++++++++++
# flattenCorrMatrix
# ++++++++++++++++++++++++++++
# cormat : matrix of the correlation coefficients
# pmat : matrix of the correlation p-values
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
cor2<-rcorr(as.matrix(sub.member.imp))
cor_table = flattenCorrMatrix(cor2$r, cor2$P)
cor_table[order(abs(cor_table$cor),decreasing = TRUE),]
```