---
title: "Final Project EDA"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(mice)
```

```{r}
member = read_csv('data/member-data-2020-stat149.csv')
head(member)
```

```{r}
dim(member)
```

```{r}
summary(member)

```
```{r}
member %>% 
  count(AnySection)
```


## Visualization
```{r}
ggplot(member, aes(USA.CAN, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("USA.CAN") 

ggplot(member, aes(JSMtot, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("JSMtot") 

ggplot(member, aes(DontPublish, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("DontPublish") 

ggplot(member, aes(MEMTYPE, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("MEMTYPE") 

ggplot(member, aes(Age, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("Age") 

ggplot(member, aes(AgeJoinedASA, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("AgeJoinedASA") 

ggplot(member, aes(Gender, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("Gender") 

ggplot(member, aes(EmploymentCategory, fill = AnySection)) +     
   scale_x_discrete(guide = guide_axis(n.dodge=3))+
   geom_bar(position = 'dodge')+ggtitle("EmploymentCategory") 

ggplot(member, aes(InChapter, fill = AnySection)) +     
   geom_bar(position = 'dodge')+ggtitle("InChapter") 


```



## Data processing


### Missing value
These columns do not have missing value. We turn yes/no to 1/0.
```{r}
member$AnySection = as.numeric(as.factor(member$AnySection))-1
member$DontPublish = as.numeric(as.factor(member$DontPublish))-1
member$MEMTYPE = as.numeric(as.factor(member$MEMTYPE))-1
member$InChapter = as.numeric(as.factor(member$InChapter))-1
member$P.SEC.BE = as.numeric(as.factor(member$P.SEC.BE))-1
member$P.SEC.BIOM = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.BIOP = as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.CNSL = as.numeric(as.factor(member$P.SEC.CNSL))-1

member$P.SEC.COMP = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.EDUC = as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.ENVR = as.numeric(as.factor(member$P.SEC.CNSL))-1
member$P.SEC.EPI = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.GOVT = as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.GRPH = as.numeric(as.factor(member$P.SEC.CNSL))-1

member$P.SEC.HPSS = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.MDD = as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.MHS = as.numeric(as.factor(member$P.SEC.CNSL))-1
member$P.SEC.MKTG = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.NPAR = as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.QP = as.numeric(as.factor(member$P.SEC.CNSL))-1

member$P.SEC.SBSS = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.SDNS= as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.SGG = as.numeric(as.factor(member$P.SEC.CNSL))-1
member$P.SEC.SI = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.SIS = as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.SLDM = as.numeric(as.factor(member$P.SEC.CNSL))-1

member$P.SEC.SOC = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.SPES= as.numeric(as.factor(member$P.SEC.BIOP))-1
member$P.SEC.SRMS = as.numeric(as.factor(member$P.SEC.CNSL))-1
member$P.SEC.SSPA = as.numeric(as.factor(member$P.SEC.BIOM))-1
member$P.SEC.TSHS = as.numeric(as.factor(member$P.SEC.BIOP))-1

```
category1: Business and Economics government 
BE, CNSL, 
category2:
```{r}
# Business and Economics Statistics
```

```{r}
member
```

USA.CAN column has 12 missing values, which are less than 1% of the total data. We will impute the missing value with the mean of this column.
```{r}
sum(is.na(member$USA.CAN)) 
member$USA.CAN[is.na(member$USA.CAN)] = 'Yes'
# any better way to convert yes/no to 1/0 ??
member$USA.CAN = as.numeric(as.factor(member$USA.CAN))-1
member %>% 
  count(USA.CAN)
```

Gender column has 2834 missing values.
EmploymentCategory column has 4216 missing values.
```{r}
sum(is.na(member$Gender)) 
sum(is.na(member$EmploymentCategory))
```

```{r}
md.pattern(member)
```
```{r}
imp <- mice(member, method = "pmm", m = 5, maxit = 50, printFlag = FALSE)
member.imp <- complete(imp)
summary(member.imp)
```

```{r}
member.na <-na.convert.mean(member)

```
```{r}
summary(member.imp)
```

```{r}
lm.vif <- lm(AnySection ~ Age, data = member)
car::vif(lm.vif)
```

